Performance-portable Parallel Programming in Computer Science Education with Kokkos

### 2020-01-23 src/5.Backend.tex
Added examples in Backend.

@@

\begin{figure}
\begin{Verbatim}[frame=leftline]

int main(int argc, char* argv[]) {
   Kokkos::initialize(argc,argv);

   int N = atoi(argv[1]);

   Foo foo;

   Kokkos::parallel_for(Kokkos::TeamPolicy<Tag1>(N,Kokkos::AUTO), foo);
   Kokkos::parallel_for("Loop2", Kokkos::TeamPolicy<Tag2>(N,Kokkos::AUTO), foo);

   Kokkos::finalize();
}

\end{Verbatim}
\caption{Declarative parallel programming provides uses pragma annotations to capture semantic information.}
\label{figOMPLike}
\end{figure}

>>>>

Explain fence guard, KOKKOS\_LAMBDA,

@@

\begin{figure}
\begin{small}
\begin{Verbatim}[frame=leftline]
int main(int argc, char* argv[]) {
  Kokkos::initialize(argc,argv);
  {
    int N = atoi(argv[1]);
    Kokkos::View<int*> a("A", N);  
    Kokkos::parallel_for(
    Kokkos::RangePolicy<Kokkos::OpenMP>(N,
    KOKKOS_LAMBDA (const int & i)
    {
      a(i)=i;
    }); 
  }
  Kokkos::finalize();
}
\end{Verbatim}
\end{small}
\caption{An application written in Kokkos shows the use of a~\emph{view}-type and parallel for loop.}
\label{fig:KokkosExample}
\end{figure}

\begin{figure}
\begin{small}
\begin{Verbatim}[frame=leftline]

template <class FunctorType, class... Traits>
class ParallelFor<FunctorType, 
    Kokkos::RangePolicy<Traits...>, 
    Kokkos::OpenMP> 
{
  ...
private:
  ... exec_range(const FunctorType& functor, 
  const Member i_beg,
  const Member i_end) 
  {
    for (Member i = i_beg; iwork < i_end; ++i){
      functor(t, i);
    }
  }

public:
  ...
  ... execute() const {(
  #pragma omp parallel num_threads(OpenMP::getPoolSize())
  {
    HostThreadTeamData& data=*(i->get_thread_data());
    ...
    range = data.get_work_partition();
    range(m_functor, range.first + m_policy.begin(),
    range.second + m_policy.begin());
  }
}

\end{Verbatim}
\end{small}
\caption{An application written in Kokkos shows a paralle for loop that .}
\label{fig:KokkosExample}
\end{figure}
